### 2024-01-09 doc/Thesis/chapter/020-theory-materials.tex
feinschliff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CIGS}
\subsection{Copper Indium Gallium Selenide} 
\gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
%It was 
\ch{CuInSe2} and \ch{CuGaSe2} were first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen}.
The potential use of \ch{CuInSe2} as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
%Already in 1975 efficiencies of cells of over 10\% were achieved.\cite{kazmerski1976thin}
Cells with efficiencies of over 10\% were achieved already by 1975\cite{kazmerski1976thin}.
Today, 
\gls{cigs} modules (multiple \gls{pv} cells in series) 
reach efficiencies of up to 16\%\cite{feurer2017cigs},
monocrystalline silicon \gls{pv} modules reach efficiencies of 14-20\%
and polycrystalline silicon \gls{pv} modules 12-17\%\cite{mcevoy2011practical}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Sol-Gel and Doctor Blading}
\subsection{Tape Casting}
%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
%
\Gls{db} coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
In roll-to-roll processes the substrate moves instead of the blade.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Copper Indium Gallium Selenide Solar Cell}
%\subsection{Copper Indium Gallium Selenide} 
\gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
%It was 
\ch{CuInSe2} and \ch{CuGaSe2} were first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen}.
The potential use of \ch{CuInSe2} as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
%Already in 1975 efficiencies of cells of over 10\% were achieved.\cite{kazmerski1976thin}
Cells with efficiencies of over 10\% were achieved already by 1975\cite{kazmerski1976thin}.
Today, 
\gls{cigs} modules (multiple \gls{pv} cells in series) 
reach efficiencies of up to 16\%\cite{feurer2017cigs},
monocrystalline silicon \gls{pv} modules reach efficiencies of 14-20\%
and polycrystalline silicon \gls{pv} modules 12-17\%\cite{mcevoy2011practical}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Sol-Gel and Doctor Blading}
\subsection{Tape Casting}
%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
%
\Gls{db} (also known as tape casting) is widely used in the textile, paper, photographic film, printing and ceramic industries.
The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
In roll-to-roll processes the substrate moves instead of the blade.

### 2024-01-09 doc/Thesis/chapter/03-experimental.tex
feinschliff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aquatic Precursor Solutions}
\label{sec:exp-sol-aq}
\gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to isopropyl aclohol (\gls{ipo}) and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the homogeneity of the resulting layer. %(in terms of what?)}. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-gls{acac} solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
%Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of \gls{zro} on the substrate.
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aquatic solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic solution}\label{sec:exp-sol-bu}
%\todo{what did you did you do percisely! It must be logical and should be followed}
Five different concentrations of the buthanolic solutions were prepared.
\ds{
\td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
}
The base recipe (\gls{1f}) was inspired by Hu~et~al.\cite{Hu2016}.
\Gls{buoh}, \gls{zrpro}, \gls{acac} and \gls{ipo}/\gls{acoh} were used as solvent, precursor, chelating agent and stabilization agent, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Blade Coating}
\label{sec:exp-db}
All glass substrates were doctor bladed manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied to create a valley in between. 
After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
%\td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Calcination of Films}\label{sec:exp-calc}
A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate the coated samples. 
The heating plate could hold temperature for a certain amount of time, but heated with a fixed rate of \oc{10}/\minutes{}.
In order to achieve a lower overall heating rate several temperature ramps and plateaus were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
This heating procedure was called HP1.
The HP1 procedure was optimized for the available hardware by a colleague working on the 
project prior to the author.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Characterization}
All characterization procedures were executed at room temperature.
All \gls{sem} micrographs were taken with a Zeiss Supra 40 with  \SI{5}{\kilo\volt} acceleration voltages.
%\td{5kV, raum temperature, vacuum???}
\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a silicon detector for visual and \gls{nir} light 
(\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged 
in Opus software. % included in the spectrometer. 
%\td{
\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer.
The diffractograms were measured for \SI{2}{\minute} in reflection mode with \ch{Cu}-$K_{\alpha}$ radiation ($\lambda$=\SI{1.541874}{\angstrom}).
%. (where are the conditions?)}
All \gls{xrd} diffractograms were taken at \SI{5}{\degree} incident angle and compared to the internal database.

@@

\section{Data Processing}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aquatic Precursor Solutions}
\label{sec:exp-sol-aq}
\gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to isopropyl aclohol (\gls{ipo}) and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the homogeneity of the resulting layer. %(in terms of what?)}. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-gls{acac} solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
%Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of \gls{zro} on the substrate.
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aquatic solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic Solution}\label{sec:exp-sol-bu}
%\todo{what did you did you do percisely! It must be logical and should be followed}
Five different concentrations of the buthanolic solutions were prepared.
\ds{
\td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
}
The base recipe (\gls{1f}) was inspired by Hu~et~al.\cite{Hu2016}.
\Gls{buoh}, \gls{zrpro}, \gls{acac} and \gls{ipo}/\gls{acoh} were used as solvent, precursor, chelating agent and stabilization agent, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tape Casting}
\label{sec:exp-db}
All glass substrates were doctor bladed manually with a smooth stainless steel wire bar coater. 
On two opposing edges adhesive tape was applied to create a valley in between. 
After the layer was applied and dried, the tape was removed and the substrate heat treated (see table~\ref{tab:heating}).
%\td{(at which T?)}.
Lower \gls{db} velocities resulted in less homogeneous layers.
Thus, the \gls{db} velocity was not altered in the manual \gls{db} process. 
One and two layers of adhesive tape were used to alter the depth of the valley.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Calcination of \ch{ZrO2}}
\label{sec:exp-calc}
A LabTech EH45C heating plate and a Naberterm LB410 muffle furnace were used to calcinate the coated samples. 
The heating plate could hold temperature for a certain amount of time, but heated with a fixed rate of \oc{10}/\minutes{}.
In order to achieve a lower overall heating rate several temperature ramps and plateaus were alternated (see table~\ref{tab:labtech}). % and figure~\ref{fig:heat}).
This heating procedure was called HP1.
The HP1 procedure was optimized for the available hardware by a colleague working on the 
project prior to the author.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% CHARACTERISATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Characterization of \ch{ZrO2} layers}
All characterization procedures were executed at room temperature.
All \gls{sem} micrographs were taken with a Zeiss Supra 40 with  \SI{5}{\kilo\volt} acceleration voltages.
%\td{5kV, raum temperature, vacuum???}
\Gls{ft}\gls{uv}/\gls{vis}/\gls{nir} transmittance and reflectance spectra (at \SI{20}{\degree} incident 
angle) were recorded with a Bruker Vertex 70 
%transmission [\%] and reflection?  which angle? 
spectrometer with a quartz beam splitter, \SI{0.5}{\milli\meter} aperture and 
Gallium-Phosphide detector for ultra violet light (\SI{303}{\nano\meter}--\SI{588}
% gallium phosphide http://dx.doi.org/10.1051/epjconf/20134800028
{\nano\meter}) and a silicon detector for visual and \gls{nir} light 
(\SI{500}{\nano\meter}--\SI{1.2}{\micro\meter}). For transmittance the light
entered the sample from the side with the layer. The \gls{uv} and \gls{vis}/\gls{nir} spectra were merged 
in Opus software. % included in the spectrometer. 
%\td{
\Gls{xrd} diffractograms were obtained with a Thermo Scientific ARL Equinox 100 X-Ray Diffractometer.
The diffractograms were measured for \SI{2}{\minute} in reflection mode with \ch{Cu}-$K_{\alpha}$ radiation ($\lambda$=\SI{1.541874}{\angstrom}).
%. (where are the conditions?)}
All \gls{xrd} diffractograms were taken at \SI{5}{\degree} incident angle and compared to the internal database.

@@

\section{Data Processing of Electrical Measurements}

### 2024-01-09 doc/Thesis/chapter/050-results-material.tex
feinschliff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray diffractogram of \ch{ZrO2}}
%\todo{of what?}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra of steel substrate (yellow; below), \gls{zro} (blue; above), $\alpha$-Fe (green; wide; idealized) and cubic-\gls{zro} (purple; narrow; idealized)\cite{gkatz1971xray} }%\td{(text in fig too small, use an offset, looks very amorphous to me)} }
	\label{fig:xrd}
	% 207_6113_10x2F_v18T40_T500v2
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spectrometry of \ch{ZrO2} layers}
%\todo{of what?}
\begin{figure}[htb]
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
		\caption{}%Transmission of \gls{zro} on glass} 
		\label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
		\caption{}%Reflection of \gls{zro} on glass} 
		\label{fig:ir-gr}
    \end{subfigure}
	\label{fig:ir}
	\caption{UV/Vis/NIR spectra of different \gls{zro} layer counts on glass 
	(a)~transmission at \SI{0}{\degree} and (b)~reflection at \SI{45}{\degree} 
	} 
%	"138_g_00L_R.dpt"  w l t "0"  , \
%	"118_g_03L_R.dpt"  w l t "3"  , \
%	"114_g_05L_R.dpt"  w l t "5"  , \
%	"130_g_10L_R2.dpt" w l t "10" , \
%	"136_g_11L_R.dpt"  w l t "11"
%	Reflection vs Reflectance and Transmission vs Transmittance
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Current Voltage Curves of \ch{ZrO2} layers} 
%\todo{of what?}
\begin{figure}
    \centering
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
		\caption{}%log good 3x4F} 
		\label{fig:iv-log-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
		\caption{}%log okay 10x1F} 
		\label{fig:iv-log-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
		\caption{}%log bad 3x3F} 
		\label{fig:iv-log-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
		\caption{}%stat good 3x4F} 
		\label{fig:iv-stat-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
		\caption{}%stat okay 10x1F} 
		\label{fig:iv-stat-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
		\caption{}%stat bad 3x3F} 
		\label{fig:iv-stat-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
		\caption{}%no current} 
		\label{fig:iv-nocurrent}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
		\caption{}%diodic} 
		\label{fig:iv-diodic}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
		\caption{}%ohmic} 
		\label{fig:iv-ohmic}
    \end{subfigure}
	%
%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
	\caption{
		Current-voltage curves and the distribution of gradients for three representative samples: insulating well (a),(d),(g), moderately (b),(e),(h), poorly (c),(f),(i); 
		(a)-(c) I-V curves with log transformed current; 
		(d)-(f) frequency histograms of the conductance with pin hole threshold marked as vertical line; 
		(g)-(i) individual I-V measurements
	}
    \label{fig:iv}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Preoptimization of Coating Procedure}
%\todo{of what?}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} velocity $v_{C}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
If the $v_{C}$ was too slow (less than \mmps{1}), no \gls{zro} layer was formed. 
The reason could be that the force exerted by the blade on the liquid is not strong enough to overcome the combination of gravity and the surface tension of the alkoxide solution.
This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
Additionally, the coating temperature affects the evaporation process together with the \gls{db} velocity $v_{C}$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray Diffractogram of \ch{ZrO2}}
%\todo{of what?}
\begin{figure}
	\centering
	\includegraphics[width=\picwidth]{Pics/xrd.png}
	\caption{XRD spectra of steel substrate (yellow; below), \gls{zro} (blue; above), $\alpha$-Fe (green; wide; idealized) and cubic-\gls{zro} (purple; narrow; idealized)\cite{gkatz1971xray} }%\td{(text in fig too small, use an offset, looks very amorphous to me)} }
	\label{fig:xrd}
	% 207_6113_10x2F_v18T40_T500v2
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spectrometry of \ch{ZrO2} Layers}
%\todo{of what?}
\begin{figure}[htb]
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
		\caption{}%Transmission of \gls{zro} on glass} 
		\label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
		\caption{}%Reflection of \gls{zro} on glass} 
		\label{fig:ir-gr}
    \end{subfigure}
	\label{fig:ir}
	\caption{UV/Vis/NIR spectra of different \gls{zro} layer counts on glass 
	(a)~transmission at \SI{0}{\degree} and (b)~reflection at \SI{45}{\degree} 
	} 
%	"138_g_00L_R.dpt"  w l t "0"  , \
%	"118_g_03L_R.dpt"  w l t "3"  , \
%	"114_g_05L_R.dpt"  w l t "5"  , \
%	"130_g_10L_R2.dpt" w l t "10" , \
%	"136_g_11L_R.dpt"  w l t "11"
%	Reflection vs Reflectance and Transmission vs Transmittance
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Current Voltage Curves of \ch{ZrO2} Layers} 
%\todo{of what?}
\begin{figure}
    \centering
	%
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=.99\textwidth]{Pics/iv/log-154-good-3x4F.png}
		\caption{}%log good 3x4F} 
		\label{fig:iv-log-good}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=.99\textwidth]{Pics/iv/log-146-okay-10x1F.png}
		\caption{}%log okay 10x1F} 
		\label{fig:iv-log-okay}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=.99\textwidth]{Pics/iv/log-156-bad-3x3F.png}
		\caption{}%log bad 3x3F} 
		\label{fig:iv-log-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
		\caption{}%stat good 3x4F} 
		\label{fig:iv-stat-good}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
		\caption{}%stat okay 10x1F} 
		\label{fig:iv-stat-okay}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
		\caption{}%stat bad 3x3F} 
		\label{fig:iv-stat-bad}
    \end{subfigure}
	%
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-nocurrent.png}
		\caption{}%no current} 
		\label{fig:iv-nocurrent}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-diodic.png}
		\caption{}%diodic} 
		\label{fig:iv-diodic}
    \end{subfigure}
    \begin{subfigure}{.32\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/146-ohmic.png}
		\caption{}%ohmic} 
		\label{fig:iv-ohmic}
    \end{subfigure}
	%
%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
	\caption{
		Current-voltage curves and the distribution of gradients for three representative samples: insulating well (a),(d),(g), moderately (b),(e),(h), poorly (c),(f),(i); 
		(a)-(c) I-V curves with log transformed current; 
		(d)-(f) frequency histograms of the conductance with pin hole threshold marked as vertical line; 
		(g)-(i) individual I-V measurements
	}
    \label{fig:iv}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pre-optimization of Coating Procedure}
%\todo{of what?}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} velocity $v_{C}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
If the $v_{C}$ was too slow (less than \mmps{1}), no \gls{zro} layer was formed. 
The reason could be that the force exerted by the blade on the liquid is not strong enough to overcome the combination of gravity and the surface tension of the alkoxide solution.
This means that behind the blade a meniscus would pull the liquid without leaving behind any solution for the gelling process. 
Additionally, the coating temperature affects the evaporation process together with the \gls{db} velocity $v_{C}$.
